Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-09-23 main.Rmd
numbats link update

Thanks to the [NUMBATS](https://www.monash.edu/news/articles/team-profile-monash-business-analytics-team) at Monash University for sharing their wisdom and experience in developing R packages, and Dr Peter Toscas [from Data61 CSIRO](https://data61.csiro.au/) for providing useful inputs on improving the analysis of the smart meter application. The package `gravitas` was built during the [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/). We would also like to thank Nicholas Spyrison for many useful discussions, sketching figures and feedback on the manuscript. More details about the package can be found at [sayani07.github.io/gravitas](https://sayani07.github.io/gravitas/). This article was created with `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown]. The Github repository, [github.com/Sayani07/paper-gravitas](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials.

>>>>

Thanks to the [NUMBATS](https://numbat.space/) at Monash University for sharing their wisdom and experience in developing R packages, and Dr Peter Toscas [from Data61 CSIRO](https://data61.csiro.au/) for providing useful inputs on improving the analysis of the smart meter application. The package `gravitas` was built during the [Google Summer of Code, 2019](https://summerofcode.withgoogle.com/archive/). We would also like to thank Nicholas Spyrison for many useful discussions, sketching figures and feedback on the manuscript. More details about the package can be found at [sayani07.github.io/gravitas](https://sayani07.github.io/gravitas/). This article was created with `knitr` [@knitr2015, @R-knitr] and `rmarkdown` [@rmarkdown2018, @R-rmarkdown]. The Github repository, [github.com/Sayani07/paper-gravitas](https://github.com/Sayani07/paper-gravitas), contains all materials required to reproduce this article and the code is also available online in the supplemental materials.
